Bird beak's elaboration and innovation

### 2022-07-21 Analysis/03.1-Elaboration_innovation_analysis[statistics].Rmd
Isolated table function

## Create the subset for all birds
all_birds_shapespace <- MCMCglmm.subsets(n = 4000, # Just run it on 500 matrices for now
      data          = shapespace_allbirds,
      posteriors    = shapespace_allbirds_posteriors,
      group         = MCMCglmm.levels(shapespace_allbirds_posteriors)[c(super_lvl, order_lvl, phylo_lvl)],
      rename.groups = c(levels(shapespace_allbirds$level1)[-1], levels(shapespace_allbirds$level2)[-1], "phylogeny")) #[-1] is because the first level is ""
## Clean garbage
rm(shapespace_allbirds_posteriors)

@@

## Create the subset for all birds
passeriformes_shapespace <- MCMCglmm.subsets( # Just run it on 500 matrices for now
      data          = shapespace_passeriformes,
      posteriors    = shapespace_passeriformes_posteriors,
      group         = MCMCglmm.levels(shapespace_passeriformes_posteriors)[c(suborder_lvl, family_lvl, phylo_lvl)],
      rename.groups = c(levels(shapespace_passeriformes$level1)[-1], levels(shapespace_passeriformes$level2)[-1], "Passeriformes")) #[-1] is because the first level is ""
## Clean garbage
rm(shapespace_passeriformes_posteriors)
```

@@

## Fucked up thing happening here:
cd("~/Packaging/dispRity/")
load_all()

@@

## Ploting fun
table.stats <- function(results) {
    ## Table results

    ## Names, comparison and size
    header <- summary(results$distances)[,c(1,2), drop = FALSE]
    head_1 <- as.data.frame(do.call(rbind, strsplit(header[,1], split = ":")))
    header <- cbind(head_1, "n" = header[, 2])
    colnames(header)[c(1,2)] <- c("Group", "Comparison")

    ## Adding the statistics
    table <- cbind(header, "distance" = summary(results$distances)[,4])
    table <- cbind(table, "ellipse sd" = results$sd[-length(results$sd)])
    table <- cbind(table, summary(results$alignments, quantiles = c(95))[, -c(1:3)])
    colnames(table)[ncol(table)-2] <- "disalignment"
    table <- cbind(table, summary(results$angles, quantiles = c(95))[, -c(1:3)])
    colnames(table)[ncol(table)-2] <- "orthogonality"
    table <- cbind(table, results$test)
    colnames(table)[ncol(table)-2] <- "Post. prob."
    rownames(table) <- NULL
    return(table)
}

@@

```{r, eval = FALSE, echo = FALSE}
load("../Data/Processed/tip_colours_super_orders.rda")
ploting.stats(ellipse_stats$super_orders_stats, col = tip_colours_super_orders)
```

```{r, eval = FALSE, echo = FALSE}
load("../Data/Processed/tip_colours_orders.rda")
ploting.stats(ellipse_stats$orders_stats, col = tip_colours_orders)
```

```{r, eval = FALSE, echo = FALSE}
load("../Data/Processed/tip_colours_passeriformes_suborder.rda")
ploting.stats(ellipse_stats$suborder_stats, col = tip_colours_passeriformes_suborder)
```

```{r, eval = FALSE, echo = FALSE}
load("../Data/Processed/tip_colours_passeriformes_family.rda")
ploting.stats(ellipse_stats$family_stats, col = tip_colours_passeriformes_family)
```

>>>>

## Create the subset for all birds
all_birds_shapespace <- MCMCglmm.subsets(
      data          = shapespace_allbirds,
      posteriors    = shapespace_allbirds_posteriors,
      group         = MCMCglmm.levels(shapespace_allbirds_posteriors)[c(super_lvl, order_lvl, phylo_lvl)],
      rename.groups = c(levels(shapespace_allbirds$level1)[-1], levels(shapespace_allbirds$level2)[-1], "phylogeny")) #[-1] is because the first level is ""
## Clean garbage
rm(shapespace_allbirds_posteriors)

@@

## Create the subset for all birds
passeriformes_shapespace <- MCMCglmm.subsets(
      data          = shapespace_passeriformes,
      posteriors    = shapespace_passeriformes_posteriors,
      group         = MCMCglmm.levels(shapespace_passeriformes_posteriors)[c(suborder_lvl, family_lvl, phylo_lvl)],
      rename.groups = c(levels(shapespace_passeriformes$level1)[-1], levels(shapespace_passeriformes$level2)[-1], "Passeriformes")) #[-1] is because the first level is ""
## Clean garbage
rm(shapespace_passeriformes_posteriors)
```

@@

# ## Fucked up thing happening here:
# cd("~/Packaging/dispRity/")
# load_all()

@@

@@
